---
title: "fiddler-crab-sizes"
format: html
editor: visual
---

```{r}
library(lterdatasampler)
library(tidyverse)
```

```{r}
head(pie_crab)
```

```{r}
# , create an exploratory (unfinalized) plot of fiddler crab carapace widths observed at the different latitudes
library(tidyverse)
unique(pie_crab$latitude)
pie_crab %>% ggplot(aes(x = size, y = latitude)) + geom_point()

```

# Graphg created NOW

```{r}
head(pie_crab)
```

```{r}

summary_table <- pie_crab %>%
  group_by(site) %>%
  summarise(
    mean_width = round(mean(size, na.rm = TRUE), 2),
    sd_width = sd(size, na.rm = TRUE),
    n = n()
  )


```

# better summary table

```{r}
library(kableExtra)

pie_crab %>%
  group_by(site) %>%
  summarise(
    mean_width = round(mean(size, na.rm = TRUE), 2),
    sd_width = sd(size, na.rm = TRUE),
    n = n()
  )  %>% 
  kable(col.names = c("Site", "Mean Width (cm)", "Standard Width (cm)", "Numer of Crabs")) %>% kable_styling(bootstrap_options = "striped" )
```

# This document is to discuss the summary statistics an d widths of the Fiddler Crabs based on elevation and sites. 

Based on Fiddler crabs and Bergmann’s rule.

Citatation:

Citation
Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb (Accessed 2021-05-27).
Johnson DS, Crowley C, Longmire K, Nelson J, Williams B, Wittyngham S. The fiddler crab, Minuca pugnax, follows Bergmann’s rule. Ecol Evol. 2019;00:1–9. https://doi.org/10.1002/ece3.5883
